Verifying Spatial Properties of Array Computations

### 2017-04-14 oopsla17/oopsla17.tex
Switch to better def style

\usepackage{hyperref}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{syntax}
\usepackage{indentfirst}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{siunitx} % For pretty-printing numeric values and SI units
                     % of measure. e.g., the tabular column type S is
                     % used to print nice-looking tables of numbers.
\sisetup{ % defaults
  group-separator={,},
  group-minimum-digits={3},
  output-decimal-marker={.},
  table-format = 6
}

@@

% Essential declarations
\theoremstyle{definition}
\newtheorem{defn}{Definition}

@@

\begin{definition}[Induction variables]
  An integer variable is a \emph{base induction variable} if it is the control
  variable of a ``\texttt{for}'' loop, incremented by $1$ per iteration. A variable
  is interpreted as an induction variable only within the scope of the loop
  body. Throughout, $i, j, k$ range over induction variables.

  A \emph{derived induction variable} is an expression of the form $a
  i + b$, \ie{}, an affine expression on an induction variable $i$.
\end{definition}

\begin{definition}[Array subscripts and indices]
  An \emph{array subscript}, denoted $a(\bar{e})$, is an expression
  which reads from an array $a$ at an \emph{index} specified by a
  comma-separated sequence of integer expressions denoted $\bar{e}$ or
  in expanded form as $(e_1, \ldots, e_n)$. An index $e_i$ is called
  \emph{relative} if the expression involves an induction variable.
  An \emph{absolute index} is a integer expression which is constant
  relative to the enclosing loop.
\end{definition}

\begin{definition}[Neighbourhood index]
\label{def:neighbour}
  For an array subscript $a(\bar{e})$ an index $e \in \bar{e}$ is a
  \emph{neighbourhood index} if $e$ is of the form $e \equiv i$, $e \equiv i +
  c$, or $e \equiv i - c$, where $c$ is an integer constant. That is, a
  neighbourhood index is a constant translation of an induction variable. (The
  relation $\equiv$ identifies terms up-to commutativity of $+$ and the inverse
  relationship of $+$ and $-$ \eg{}, $(-b) + i \equiv i - b$).
\end{definition}

@@

\begin{defn}{(\emph{Region})}
  A region \region{N} is an $N$-dimensional index scheme
  (\ie{}, $\region{N} \subseteq \mathcal{P}(\bz)^N)$ defined as the smallest set satisfying the following:
%
  \begin{enumerate}
    \item If $R$ is in $\textit{Interval}^N$, then $R$ is in \region{N}.
    \item If $R$ and $S$ are in \region{N}, then so are $R \cap S$ and
      $R \cup S$.
  \end{enumerate}
\end{defn}

@@

\begin{defn}{}
  $\mathsf{Mult}$ and $\mathsf{Approx}$ are parametric labelled variant types
  with injections given by their definition:
%
  \begin{align*}
    \mathsf{Mult} \;\; a \;\; &
      \triangleq \mathsf{mult} \; a \;\mid\; \mathsf{only} \; a \\
    \mathsf{Approx} \;\; a \;\; &
      \triangleq \mathsf{exact} \; a \;\mid\; \mathsf{lower} \; a \;\mid\;
        \mathsf{upper} \; a
  \end{align*}
%
  \eg{}, $\mathsf{lower}$ is an injection $\mathsf{lower} : a \to \mathsf{Approx}
  \; a$ etc.
  These will be used in the following subsection to give meaning to the
  specification modifiers for approximation and multiplicity.
\end{defn}

>>>>

\usepackage{hyperref}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{syntax}
\usepackage{indentfirst}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{siunitx} % For pretty-printing numeric values and SI units
                     % of measure. e.g., the tabular column type S is
                     % used to print nice-looking tables of numbers.
\sisetup{ % defaults
  group-separator={,},
  group-minimum-digits={3},
  output-decimal-marker={.},
  table-format = 6
}

@@

\theoremstyle{defn}
\newtheorem{defn}{Definition}

@@

\begin{defn}[Induction variables]
  An integer variable is a \emph{base induction variable} if it is the control
  variable of a ``\texttt{for}'' loop, incremented by $1$ per iteration. A variable
  is interpreted as an induction variable only within the scope of the loop
  body. Throughout, $i, j, k$ range over induction variables.

  A \emph{derived induction variable} is an expression of the form $a
  i + b$, \ie{}, an affine expression on an induction variable $i$.
\end{defn}

\begin{defn}[Array subscripts and indices]
  An \emph{array subscript}, denoted $a(\bar{e})$, is an expression
  which reads from an array $a$ at an \emph{index} specified by a
  comma-separated sequence of integer expressions denoted $\bar{e}$ or
  in expanded form as $(e_1, \ldots, e_n)$. An index $e_i$ is called
  \emph{relative} if the expression involves an induction variable.
  An \emph{absolute index} is a integer expression which is constant
  relative to the enclosing loop.
\end{defn}

\begin{defn}[Neighbourhood index]
\label{def:neighbour}
  For an array subscript $a(\bar{e})$ an index $e \in \bar{e}$ is a
  \emph{neighbourhood index} if $e$ is of the form $e \equiv i$, $e \equiv i +
  c$, or $e \equiv i - c$, where $c$ is an integer constant. That is, a
  neighbourhood index is a constant translation of an induction variable. (The
  relation $\equiv$ identifies terms up-to commutativity of $+$ and the inverse
  relationship of $+$ and $-$ \eg{}, $(-b) + i \equiv i - b$).
\end{defn}

@@

\begin{defn}[Region]
  A region \region{N} is an $N$-dimensional index scheme
  (\ie{}, $\region{N} \subseteq \mathcal{P}(\bz)^N)$ defined as the smallest set satisfying the following:
%
  \begin{enumerate}
    \item If $R$ is in $\textit{Interval}^N$, then $R$ is in \region{N}.
    \item If $R$ and $S$ are in \region{N}, then so are $R \cap S$ and
      $R \cup S$.
  \end{enumerate}
\end{defn}

@@

\begin{defn}
  $\mathsf{Mult}$ and $\mathsf{Approx}$ are parametric labelled variant types
  with injections given by their definition:
%
  \begin{align*}
    \mathsf{Mult} \;\; a \;\; &
      \triangleq \mathsf{mult} \; a \;\mid\; \mathsf{only} \; a \\
    \mathsf{Approx} \;\; a \;\; &
      \triangleq \mathsf{exact} \; a \;\mid\; \mathsf{lower} \; a \;\mid\;
        \mathsf{upper} \; a
  \end{align*}
%
  \eg{}, $\mathsf{lower}$ is an injection $\mathsf{lower} : a \to \mathsf{Approx}
  \; a$ etc.
  These will be used in the following subsection to give meaning to the
  specification modifiers for approximation and multiplicity.
\end{defn}
